An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-29 VLDB2026/main.tex
Update main.tex

	\setlength{\textfloatsep}{0.1cm}
	\setlength{\floatsep}{0cm}
	\renewcommand{\arraystretch}{0.9}
	\begin{table}[t]
		\centering
		\setlength{\abovecaptionskip}{0.1cm}
		\setlength{\belowcaptionskip}{-0.1cm}
		\setlength{\textfloatsep}{0.1cm}
		\caption{Comparison of RF-ANN search algorithms}
		\small	% 只会影响当前组的内容
		\label{tab:range_algo}
		\begin{tabular}{|c|c|c|c|}
			\hline
			\textbf{Algorithm} & \textbf{Base} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
			\hline
			DSG & Graph & Y & N \\
			iRange & Graph & N & Y \\
			SeRF & Graph & Y & Y \\
			UNIFY & Graph & Y & Y \\
			WinFilter & Graph & N & Y  \\
			\hline
		\end{tabular}

		\footnotesize{
			\begin{minipage}{\linewidth}
				\textsuperscript{Y} Support, 
				\textsuperscript{N} Unsupport.
				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
			\end{minipage} 
			\vspace{-0.1cm}
		}

@@

	Table~\ref{tab:datasets_combined} summarizes the key characteristics of all datasets. In particular, we report the Local Intrinsic Dimensionality (LID)~\cite{Lid}, a commonly used metric to quantify dataset hardness. Following the standard evaluation protocol~\cite{LID2}, we randomly sample 10,000 data points from each dataset for LID computation. A higher LID indicates greater intrinsic complexity.

	\setlength{\textfloatsep}{0.1cm}
	\setlength{\floatsep}{0cm}
	\renewcommand{\arraystretch}{0.9}
	\begin{table}[t]
		\centering

		\setlength{\abovecaptionskip}{0cm}
		\setlength{\belowcaptionskip}{-0.3cm}
		\caption{Datasets}

@@

	\begin{figure*}
		\centering
		\setlength{\abovecaptionskip}{0cm}
		\setlength{\belowcaptionskip}{-0.4cm}
		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
		\caption{Single-Attribute Building and Query (single thread) }
		\label{fig:exp_1_1_SingleLabel_1thread}
	\end{figure*}

	\begin{figure*}
		\centering
		\setlength{\abovecaptionskip}{0cm}
		\setlength{\belowcaptionskip}{-0.4cm}
		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
		\caption{Single-Attribute Building and Query (16 threads)}
		\label{fig:exp_1_2_SingleLabel_16thread}
	\end{figure*}

@@

	\begin{figure*}
		\centering
		\setlength{\abovecaptionskip}{0.0cm}
		\setlength{\belowcaptionskip}{-0.4cm}
		\includegraphics[width=0.95\textwidth]{figures/exp/exp_4_1_MultiLabel_1thread.pdf}
		\caption{Multi-attribute build and query (single thread)}
		\label{fig:exp_4_1_MultiLabel_1thread}
	\end{figure*}

	\begin{figure*}
		\centering
		\setlength{\abovecaptionskip}{0.0cm}
		\setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
		\caption{Effect of attribute distribution on query performance (single thread)}
		\label{fig:exp_3_1}
	\end{figure*}

@@

	\begin{figure*}
		\centering
		\setlength{\abovecaptionskip}{-0.1cm}
		\setlength{\belowcaptionskip}{-0.4cm}
		\includegraphics[width=0.95\textwidth]{figures/exp/exp_6_1.pdf}
		\caption{Effect of dataset on Query}
		\label{fig:exp_6_1}
	\end{figure*}

@@

	% \begin{figure*}[htbp]
		%     \centering
		%     \setlength{\abovecaptionskip}{0cm}
		%     \setlength{\belowcaptionskip}{-0.4cm}
		%     \includesvg[width=\textwidth]{figures/exp/exp_8_3.svg}
		%     \caption{Dataset Effect on RF-ANN Search}
		%     \label{fig:exp_8_3}
		% \end{figure*}
	\begin{figure*}[htbp]
		\centering
		\setlength{\abovecaptionskip}{0cm}
		\setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=0.80\textwidth]{figures/exp/exp_8_3.pdf}
		\caption{Dataset Effect on RF-ANN Search}
		\label{fig:exp_8_3}
	\end{figure*}

>>>>

	\renewcommand{\arraystretch}{0.9}
	\begin{table}[t]
		\centering

		\setlength{\textfloatsep}{0.1cm}
		\caption{Comparison of RF-ANN search algorithms}
		\small	% 只会影响当前组的内容
		\label{tab:range_algo}
		\begin{tabular}{|c|c|c|c|}
			\hline
			\textbf{Algorithm} & \textbf{Base} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
			\hline
			DSG & Graph & Y & N \\
			iRange & Graph & N & Y \\
			SeRF & Graph & Y & Y \\
			UNIFY & Graph & Y & Y \\
			WinFilter & Graph & N & Y  \\
			\hline
		\end{tabular}

		\footnotesize{
			\begin{minipage}{\linewidth}
				\textsuperscript{Y} Support, 
				\textsuperscript{N} Unsupport.
				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
			\end{minipage}

		}

@@

	Table~\ref{tab:datasets_combined} summarizes the key characteristics of all datasets. In particular, we report the Local Intrinsic Dimensionality (LID)~\cite{Lid}, a commonly used metric to quantify dataset hardness. Following the standard evaluation protocol~\cite{LID2}, we randomly sample 10,000 data points from each dataset for LID computation.The higher the LID value, the harder the dataset.

	\renewcommand{\arraystretch}{0.9}
	\begin{table}[t]
		\centering

		\caption{Datasets}

@@

		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
		\caption{Single-Attribute Building and Query (single thread) }
		\label{fig:exp_1_1_SingleLabel_1thread}
	\end{figure*}

		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
		\caption{Single-Attribute Building and Query (16 threads)}
		\label{fig:exp_1_2_SingleLabel_16thread}
	\end{figure*}

@@

		\includegraphics[width=0.95\textwidth]{figures/exp/exp_4_1_MultiLabel_1thread.pdf}
		\caption{Multi-attribute build and query (single thread)}
		\label{fig:exp_4_1_MultiLabel_1thread}
	\end{figure*}

		\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
		\caption{Effect of attribute distribution on query performance (single thread)}
		\label{fig:exp_3_1}
	\end{figure*}

@@

	\begin{figure*}
		\centering
		\includegraphics[width=0.95\textwidth]{figures/exp/exp_6_1.pdf}
		\caption{Effect of dataset on Query}
		\label{fig:exp_6_1}
	\end{figure*}

@@

	\begin{figure*}[htbp]
		\centering
		\includegraphics[width=0.80\textwidth]{figures/exp/exp_8_3.pdf}
		\caption{Dataset Effect on RF-ANN Search}
		\label{fig:exp_8_3}
	\end{figure*}
